\LARGE \bf Mean Estimation from One-Bit Measurements

### 2019-12-23 distributed-estimation.tex
corrected various typos

Yet Theorem~\ref{theorem:non-adaptive-minimax}
limits non-adaptive strategies in stronger ways.
%%
%% \subsection{Non-existence of a Uniformly Optimal Strategy}
%%
Under the density models we have considered, with the additional
Assumption~\ref{assump:failure_rate}, we can show stronger
optimality results that adaptivity is essential for achieving
optimal convergence guarantees.
Recall the transformation~\eqref{eq:eta_def} of the
hazard rate function, $\eta(x) = \frac{f^2(x)}{F(x)(1 - F(x))}$, which
has unique maximum at $x = 0$ under Assumption~\ref{assump:failure_rate}.
When each detection region $A_n$ consists of a bounded number
of intervals, the next theorem
shows that
the optimal minimal risk $1/\eta(0)$ can
only be attained at finitely many points within $\Theta$.
In particular, distinct from the adaptive setting, no distributed
estimation scheme can achieve asymptotic variance $\eta(0)$
uniformly in $\theta \in \Theta$.

@@

We now consider consider a restricted case where each detection region is a
half-open interval, i.e., the $i$th message is obtained by comparing $X_i$
against a single threshold. Under adaptive signal acquisition,
this is sufficient for asymptotic optimality;
in non-adaptive settings, it is not sufficient, though we may characterize
a few additional optimality results.
%% As we explain next, the existence of a density
%% for the sequence of thresholds is enough to establish local asymptotic
%% normality and leads to a closed form expression for the precision parameter
%% and the ARE.
Assume now that each $B_i$ is of the form
\begin{equation}
  \label{eq:threshold_message}
  B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
    -1 & X_i > t_i,
  \end{cases}  
\end{equation}
where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder. In
other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and
$\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$. It follows that
\begin{equation}
  L_n(A_1,\ldots,A_n;\theta)
  = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
  \label{eq:Ln_threshold}
\end{equation}
A natural condition for the existence of the limit \eqref{eq:Ln_threshold}
as $n\to \infty$ is that the empirical distribution of the threshold values
converges to a probability measure. Specifically, for an interval $I \subset
\mathbb R$ define
\begin{equation*}
  \lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
\end{equation*}
Then an investigation of the proof of
Theorem~\ref{theorem:non-adaptive-minimax} in
Section~\ref{sec:proof-non-adaptive-minimax}, specifically
Sec.~\ref{sec:proof-lan-bits} and the bounds~\eqref{eqn:h-fourth}, show that
as $\eta(t) \le \eta(0)$ for all $t \in \R$ under
Assumption~\ref{assump:failure_rate}, the following corollary follows. (The
corollary relies on local asymptotic normality~\cite[Ch.~7]{VanDerVaart98};
see Appendix~\ref{sec:proof-sgd-regular} for some brief discussion of such
conditions.)
\begin{cor} \label{cor:LAN_thresh}
  Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that
  $\lambda_n$ converges (weakly) to a probability measure $\lambda(dt)$ on
  $\mathbb R$. Then the conclusions of
  Theorem~\ref{theorem:non-adaptive-minimax} apply with
  %% $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a
  %% LAN family with precision parameter
  \begin{equation*}
    \kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
  \end{equation*}
  Moreover, the family of laws of $\{B_i = \sgn(X_i - t_i)\}_{i = 1}^n$
  under $\{P_\theta\}_{\theta \in \Theta}$ is locally asymptotically normal
  with information $\kappa(\theta)$.
\end{cor}

>>>>

Yet, Theorem~\ref{theorem:non-adaptive-minimax}
limits non-adaptive strategies in stronger ways.
%%
%% \subsection{Non-existence of a Uniformly Optimal Strategy}
%%
Under the density models we have considered, with the additional
Assumption~\ref{assump:failure_rate}, we can show stronger
optimality results that adaptivity is essential for achieving
optimal convergence guarantees.
Recall the transformation~\eqref{eq:eta_def} of the
hazard rate function, $\eta(x) = \frac{f^2(x)}{F(x)(1 - F(x))}$, which
has unique maximum at $x = 0$ under Assumption~\ref{assump:failure_rate}.
When each detection region $A_n$ consists of a bounded number
of intervals, the next theorem shows that
the minimal risk $1/\eta(0)$ can
only be attained at finitely many points within $\Theta$.
In particular, distinct from the adaptive setting, no distributed
estimation scheme can achieve asymptotic variance $\eta(0)$
uniformly in $\theta \in \Theta$.

@@

We now consider consider a restricted case where each detection region is a
half-open interval, i.e., the $i$th message is obtained by comparing $X_i$
against a single threshold. Under adaptive signal acquisition,
this is sufficient for asymptotic optimality;
in non-adaptive settings, it is not sufficient, though we may characterize
a few additional optimality results.
%% As we explain next, the existence of a density
%% for the sequence of thresholds is enough to establish local asymptotic
%% normality and leads to a closed form expression for the precision parameter
%% and the ARE.
Assume now that each $B_i$ is of the form
\begin{equation}
  \label{eq:threshold_message}
  B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i< t_i, \\
    -1 & X_i > t_i,
  \end{cases}  
\end{equation}
where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder. In
other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and
$\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$. It follows that
\begin{equation}
  L_n(A_1,\ldots,A_n;\theta)
  = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
  \label{eq:Ln_threshold}
\end{equation}
A natural condition for the existence of the limit \eqref{eq:Ln_threshold}
as $n\to \infty$ is that the empirical distribution of the threshold values
converges to a probability measure. Specifically, for an interval $I \subset
\mathbb R$, define
\begin{equation*}
  \lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
\end{equation*}
Then an investigation of the proof of
Theorem~\ref{theorem:non-adaptive-minimax} in
Section~\ref{sec:proof-non-adaptive-minimax}, specifically
Sec.~\ref{sec:proof-lan-bits} and the bounds~\eqref{eqn:h-fourth}, show that
as $\eta(t) \le \eta(0)$ for all $t \in \R$ under
Assumption~\ref{assump:failure_rate}, the following corollary follows. (The
corollary relies on local asymptotic normality~\cite[Ch.~7]{VanDerVaart98};
see Appendix~\ref{sec:proof-sgd-regular} for some brief discussion of such
conditions.)
\begin{cor} \label{cor:LAN_thresh}
  Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that
  $\lambda_n$ converges (weakly) to a probability measure $\lambda$ on
  $\mathbb R$. Then the conclusions of
  Theorem~\ref{theorem:non-adaptive-minimax} apply with
  %% $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a
  %% LAN family with precision parameter
  \begin{equation*}
    \kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
  \end{equation*}
  Moreover, the family of laws of $\{B_i = \sgn(X_i - t_i)\}_{i = 1}^n$
  under $\{P_\theta\}_{\theta \in \Theta}$ is locally asymptotically normal
  with information $\kappa(\theta)$.
\end{cor}
